\textbf{ Spectrophotometric parallaxes with linear models:\\ Accurate distances for luminous red-giant stars }

### 2018-10-15 paper/sp.tex
precision plot

% HOGG: NEW FIGURE -- put some words in the text about the figure. 
\begin{figure}
\centering
~\hfill\includegraphics[width=0.8\textwidth]{./precision.pdf}\hfill~
\caption{some smart words :) \label{fig:precision}}
\end{figure}

@@

>>>>

@@

It is interesting and valuable to compare the spectrophotometric parallax precision to
the astrometric parallax precision.
\figurename~\ref{fig:precision} compares uncertainties between the spectrophotometric
outputs and the astrometric inputs
(and recall that information is proportional to the inverse square of the uncertainty).
The brief summary is that the spectrophotometric parallaxes are more precise (and even
far more precise) than the astrometric parallaxes for stars further than a few kpc from
the Sun.
This is not unexpected; \gaia\ parallax uncertainties are in the 0.1-mas range, whereas
our uncertainties are in the ten-percent range.
\begin{figure}
\centering
~\hfill\includegraphics[width=0.8\textwidth]{./precision.pdf}\hfill~
\caption{Comparison of precisions between the spectrophotometric parallaxes and
the photometric parallaxes, as a function of magnitude and heliocentric distance.
Note that the spectrophotometric estimates are more precise for most stars.
The information content of a parallax estimate (or any measurement)
is proportional to the inverse-square of the uncertainty.\label{fig:precision}}
\end{figure}
